Fast-Match: Fast and robust feature matching on large images

### 2014-11-08 paper.tex
Added tests on crops from graffiti set

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{ruler}
\usepackage{color}
\usepackage{footnote}
\usepackage{multirow} 
\usepackage{cite}
\usepackage[draft]{hyperref}
\usepackage{balance}
\usepackage{subcaption}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{amssymb}
\usepackage{bbm}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
%\usepackage{authblk}
\pdfminorversion=4
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

\newcommand{\twopartdef}[4]
{
	\left\{
		\begin{array}{ll}
			#1 & \mbox{if } #2 \\
			#3 & \mbox{if } #4
		\end{array}
	\right.
}

%===========================================================
\begin{document}
\pagestyle{headings}
\mainmatter

@@

%===========================================================
\title{Fast-Match:\\Fast and Robust Feature Matching on Large Images}
\titlerunning{ACCV-14 submission ID \ACCV14SubNumber}
\authorrunning{ACCV-14 submission ID \ACCV14SubNumber}

\author{Anonymous ACCV 2014 submission}
\institute{Paper ID \ACCV14SubNumber}

@@

\begin{abstract}
    Consumer digital cameras and camera phones produce images that often exceed 10 megapixels. Yet computing and matching local features in images of this size can easily take more than twenty seconds using fast matching algorithms. This is much too slow for interactive applications and much too expensive for large scale image operations. We introduce \emph{Fast-Match}, an algorithm designed to swiftly match large images without compromising on matching precision or recall. \emph{Fast-Match} derives its speed from only computing features in those parts of the image that can be confidently matched. We show that \emph{Fast-Match} is an order of magnitude faster than \emph{Ratio-Match}, yet often doubles the precision on difficult to match image pairs at equal recall. In addition we prove that when one image is known in advance, \emph{Fast-Match} can achieve linear performance $O(n)$ in the number of feature points $n$.
\end{abstract}

@@

Another inspiration for the design of \emph{Fast-Match} is \emph{Patch-Match} as introduced by Barnes et al.~\cite{barnes2009patchmatch}. Like \emph{Fast-Match}, \emph{Patch-Match} is an iterative algorithm for fast image matching, but unlike \emph{Fast-Match}, which uses sparse local image features, \emph{Patch-Match} is designed for dense image features. It works by randomly creating a set of matches from both images and then iteratively improving it.

@@

\begin{figure}[tb]
    \centering
    \begin{subfigure}[t]{0.5\columnwidth}
        \includegraphics[width=1\columnwidth]{images/Illinois-fastmatch}
    \end{subfigure}%
    ~%\vspace{1.5 mm}
    \begin{subfigure}[t]{0.5\columnwidth}
        \includegraphics[width=1\columnwidth]{images/Illinois-ratiomatch}
    \end{subfigure}%
    \caption{The 50 best matches by the proposed \emph{Fast-Match} algorithm (left) and the \emph{Ratio-Match} algorithm \cite{lowe2004sift} (right). The lines between the image pairs denote a match as proposed by the algorithm. For \emph{Fast-Match} the areas where local features were computed are marked with blue squares in the right image.}
    \label{fig:match_example}
\end{figure}

@@

\subsection{Initiating Seeds}
\label{seeds}
%
Depending on the scenario, several strategies can be used to obtain a set of initial seed matches. For the case of matching a pair of two images we can get a rough group of seed matches by matching the thumbnails of the two images with for example \emph{Ratio-Match}. However if we were matching images in a series, such as frames from a movie we could instead make use of a subset of the matches from the last frame to seed \emph{Fast-Match} on the next. In practice we have found it efficient to resize both images to thumbnails of $300\times 300$ pixels and use ratio match to obtain a set of matches and ratios that we then threshold with the confidence threshold $\tau$ to obtain the initial seed matches.

@@

Lowe and others have shown that the distance between two SIFT descriptors is much less indicative of a true correspondence than the ratio between the best and second best match \cite{lowe2004sift,mikolajczyk2005performance,moreels2007evaluation,rabin2009statistical}. This ratio is more formally defined as follows: If we let $f_q$ be a feature in the \emph{query image} and $f_t, f_b$ be the two nearest neighbours of $f_q$ in the \emph{target image} then the ratio $r$ is defined as follows:
\begin{align*}
    r &= %\text{r}(f_{q}, (f_t, f_b)) \\
        &= \frac{d(f_{q}, f_{t})}{d(f_{q}, f_{b})}.
\end{align*}
Here $d(f_i,f_j)$ is the distance between the features $f_i$ and $f_j$. For SIFT this is the Euclidean distance. The distance between two feature points is greater when the feature points resemble each other less. For this reason we have higher confidence in a match with a low $r$-value. Using $r$ as a measure of match confidence presumes that we expect each feature in the \emph{target image} to have at most one true correspondence in the \emph{target image}. Intuitively if we try to find a match for a feature $f_i$ in an image that does not have any true correspondences, then we would expect the two closest neighbours to be roughly equally well matched with $f_i$. For this reason we attribute high confidence to matches where the closest neighbour is dramatically closer to $f_i$ than the second closest neighbour and discard the rest.

@@

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.75\columnwidth]{images/exploration}
\caption{Exploration of features based on a match. The areas shaded blue are the areas that were searched to obtain the match. The areas shaded green are candidate areas for obtaining more matches.}
\label{fig:exploration}
\end{figure}

@@

\section{Experimental Setup}
\label{experiments}
%
We evaluate \emph{Fast-Match} over 3024 image pairs featuring various 3D objects at different angles to measure precision and recall, as well as two pairs of images with high pixel counts to measure performance in terms of speed. We compare the algorithm to the standard \emph{Ratio-Match} \cite{lowe2004sift} as well as the newer \emph{Mirror-Match} \cite{arnfred2013mirror}. These two algorithms were selected because they are magnitudes faster than the fastest geometric algorithms while at the same time providing robust matches.

\subsection{Evaluation of Fast-Match on 3D Objects}
\label{3dobjects}
%
The 3D Objects dataset by Moreels and Perona \cite{moreels2007evaluation} allows us to experimentally compare matching algorithms over a large range of object and surface types rotated on a turnstile and photographed from every angle in increments of 5 degrees. 15 objects from the dataset are shown in Figure~\ref{fig:3d_objects}.  We use images of 84 different objects photographed under three different lighting conditions at 12 different angle intervals, conducting experiments with a total of 3024 image pairs. All photos a taken with a consumer camera in 3.1 mega pixel resolution.

@@

    \caption{15 objects from the 3D Objects dataset by Moreels
    and Perona \cite{moreels2007evaluation}.}
    \label{fig:3d_objects}
\end{figure}

@@

To compute the total number of possible true correspondences, we take each feature in a \emph{query image} and count how many of them have a feature in the \emph{target image} which would satisfy the epipolar constraints. When using this dataset, features with no correspondences were not included in the set of features for testing, so as to avoid matching non-moving background and foreground objects.

We evaluate all matching algorithms from our framework on the 3D Objects dataset by matching images at different angular intervals. For each object we pick the \emph{query} image as the image taken at 10 degrees rotation for calibration stability.  We then match this image with the same object turned an additional $\Delta$ degrees, $\Delta \in \{5, 10, \ldots, 60\}$.  For every angle interval we compare images taken under 3 different lighting conditions as provided by the dataset. We include all objects in the database for which photos at 5 degree angle intervals are available except for the ``Rooster'' and ``Sponge'' objects due to image irregularities.

\subsection{Configuration of \emph{Fast-Match}}
%
The central parameters of \emph{Fast-Match} are the confidence threshold $\tau$ for selecting seed matches and the final confidence threshold applied to the total set of matches. For the experiments on the 3D Objects we let $\tau = 0.9$ and created precision/recall plots by varying the confidence threshold over the final set of matches.

To achieve a good balance between speed and robustness we let the region in which we extract features be a square with a side length of 90 pixels. On empirical tests we found that anything smaller would result in decreased performance while much bigger regions would decrease speed. The 90 pixel window is split in to nine smaller squares (see also Figure~\ref{fig:exploration}). When a seed match falls in any of these squares we match only the features within the smaller square. We let both the regions and the smaller squares overlap each other at all edges with 25 pixels in order to capture feature points lying close to an edge. For the image we have already cached we find all features within a radius of 50 pixels of the seed match.

\section{Results}
\label{results}
%
\begin{figure}[t]
\centering
\includegraphics[width=1\columnwidth]{images/grid_match_all}
\caption{Results for the 3D Objects dataset. Each plot contains data accumulated from 84 objects photographed under 3 different lighting conditions.}
\label{fig:all_objects}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=1\columnwidth]{images/timings}
    \caption{Running times of different variations of \emph{Fast-Match} and \emph{Ratio-Match}. The top plot shows results for two 10~MPixel images two 3~Mpixel images is used for the comparison at the bottom. From the left, the first two results presume a precached image while the rest do not require knowing any inputs beforehand. The image pairs used be seen in Figure~\ref{fig:match_example}.}
    \label{fig:timings}
\end{figure}

@@

We have introduced \emph{Fast-Match} in two forms, a general and a retrieval variation. The retrieval variation assumes that we know one of the images that we are matching ahead of time in order to pre-cache feature points. The general variation has no assumptions and performs the pre-caching of feature points online instead. 
We have proven that while the general variation has a computational complexity of $O(n \log n)$ with $n$ being the number of feature points, the retrieval variation will on average run in $O(n)$.
From experiments on large images we have shown that \emph{Fast-Match} can be a magnitude faster than \emph{Ratio-Match} while providing comparable results. We further compared \emph{Fast-Match} to \emph{Ratio-Match} and \emph{Mirror-Match} using images of rotated 3D objects to demonstrate that \emph{Fast-Match} outperforms the other algorithms significantly over 3024 image pairs and in most cases doubles the matching precision at similar recall rates.
\emph{Fast-Match} is particularly applicable in cases where we are interested in matching one image to multiple large images, in which case we can quickly pre-cache the image and use this data for each of the other images.

\bibliographystyle{splncs}
\bibliography{bibliography}
\end{document}

>>>>

\documentclass[10pt,twocolumn,letterpaper]{article}
\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath,amssymb} % define this before the line numbering.
%\usepackage{ruler}
\usepackage{color}
\usepackage{footnote}
\usepackage{multirow} 
\usepackage{cite}
\usepackage[draft]{hyperref}
\usepackage{balance}
\usepackage{subcaption}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{amssymb}
\usepackage{bbm}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
%\usepackage{authblk}
\pdfminorversion=4
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

\newcommand{\twopartdef}[4]
{
	\left\{
		\begin{array}{ll}
			#1 & \mbox{if } #2 \\
			#3 & \mbox{if } #4
		\end{array}
	\right.
}
\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi
%===========================================================
\begin{document}
%\pagestyle{headings}

@@

%===========================================================
\title{Fast-Match: Fast and robust feature matching on large images}

\author{Anonymous CVPR 2015 submission}

@@

\begin{abstract}
    Both consumer cameras and camera phones produce images that often exceed 10 megapixels. Yet computing and matching local features in images of this size can easily take more than twenty seconds using fast matching algorithms. This is much too slow for interactive applications and much too expensive for large scale image operations. We introduce \emph{Fast-Match}, an algorithm designed to swiftly match large images without compromising on matching precision or recall. \emph{Fast-Match} derives its speed from only computing features in those parts of the image that can be confidently matched. We show that \emph{Fast-Match} is an order of magnitude faster than \emph{Ratio-Match}, yet often doubles the precision on difficult to match image pairs at equal recall. In addition we prove that when one image is known in advance, \emph{Fast-Match} can achieve linear performance $O(n)$ in the number of feature points $n$.
\end{abstract}

@@

@@

\begin{figure}[tb]
    \centering
    \begin{subfigure}[t]{0.5\columnwidth}
        \includegraphics[width=1\columnwidth]{images/Illinois-fastmatch}
    \end{subfigure}%
    ~%\vspace{1.5 mm}
    \begin{subfigure}[t]{0.5\columnwidth}
        \includegraphics[width=1\columnwidth]{images/Illinois-ratiomatch}
    \end{subfigure}%
    \caption{The 50 best matches by the proposed \emph{Fast-Match} algorithm (left) and the \emph{Ratio-Match} algorithm \cite{lowe2004sift} (right). The lines between the image pairs denote a match as proposed by the algorithm. For \emph{Fast-Match} the zones of the right image where local features were computed has been marked with a blue square.}
    \label{fig:match_example}
\end{figure}

@@

\subsection{Initiating Seeds}
\label{seeds}
%
Depending on the scenario, several strategies can be used to obtain a
set of initial seed matches. In practice we have found it efficient to
resize both images to thumbnails and use
\emph{Ratio-Match} to obtain a set of matches and ratios that we then
threshold with the confidence threshold $\tau$ to obtain the initial
seed matches. The thumbnails created need to be sized so they on one hand ensure that objects of interest are still detectable by a keypoint detector while on the other remain small to ensure that we find matches efficiently. We determine empirically that a thumbnail size of $300\times300$ pixels maintains a good balance between speed and accuracy. We found this size to be independent of the original image size as long as we are matching images that are bigger than one megapixel.

@@

Lowe and others have shown that the distance between two SIFT descriptors is much less indicative of a true correspondence than the ratio between the best and second best match \cite{lowe2004sift,mikolajczyk2005performance,moreels2007evaluation,rabin2009statistical}. This ratio is more formally defined as follows: If we let $f_q$ be a feature in the \emph{query image} and $f_t, f_b$ be the two nearest neighbours of $f_q$ in the \emph{target image} then the ratio $r$ is defined as follows:
\begin{align*}
    r %\text{r}(f_{q}, (f_t, f_b)) \\
        &= \frac{d(f_{q}, f_{t})}{d(f_{q}, f_{b})}.
\end{align*}
Here $d(f_i,f_j)$ is the distance between the features $f_i$ and $f_j$. For SIFT this is the Euclidean distance. The distance between two feature points is greater when the feature points resemble each other less. For this reason we have higher confidence in a match with a low $r$-value. Using $r$ as a measure of match confidence presumes that we expect each feature in the \emph{target image} to have at most one true correspondence in the \emph{target image}. Intuitively if we try to find a match for a feature $f_i$ in an image that does not have any true correspondences, then we would expect the two closest neighbours to be roughly equally well matched with $f_i$. For this reason we attribute high confidence to matches where the closest neighbour is dramatically closer to $f_i$ than the second closest neighbour and discard the rest.

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.75\columnwidth]{images/exploration}
\caption{Exploration of features based on match. The areas shaded blue are the areas that were searched to obtain the match. The areas shaded green are candidate areas for obtaining more matches.}
\label{fig:exploration}
\end{figure}

@@

@@

\section{Experimental Setup}
\label{experiments}
%
To evaluate \emph{Fast-Match} on three sets of data. We use a dataset of 3024 image pairs featuring various 3D objects at different angles and lighting conditions to measure matching performance for real life objects when lighting and perspective changes. To evaluate the performance of \emph{Fast-Match} when only part of (or none of) the scene is shared between an image pair we conduct experiments on 400 random crops with different degree of image overlap taken from 4 image pairs, creating a challenging test set where large part of the images consists of background clutter similar in nature to the subject being matched. Finally we time the algorithm on two pairs of images with high pixel counts to measure performance in terms of speed.

We compare the algorithm to the standard \emph{Ratio-Match} \cite{lowe2004sift} as well as the newer \emph{Mirror-Match} \cite{arnfred2013mirror}. We exclude the geometric algorithms discussed in related works from comparison because even the fastest cases are two to three magnitudes slower than \emph{Ratio-Match} and as such are too time consuming to use when matching features in large images. Both \emph{Ratio-Match} and \emph{Mirror-Match} however have shown good results in matching applications while both being fast enough to compare on larger images.

\subsection{Evaluation of Fast-Match on 3D Objects}
\label{3dobjects}
%
The 3D Objects dataset by Moreels and Perona \cite{moreels2007evaluation} allows us to experimentally compare matching algorithms over a large range of object and surface types rotated on a turnstile and photographed from every angle in increments of 5 degrees. 15 objects from the dataset are shown in Figure~\ref{fig:3d_objects}.  We use images of 84 different objects photographed under three different lighting conditions at 12 different angle intervals, conducting experiments with a total of 3024 image pairs. All photos a taken with a consumer camera in 3.1 megapixel resolution.

@@

    \caption{15 objects from the 3D Objects dataset by Moreels
    and Pietro \cite{moreels2007evaluation}.}
    \label{fig:3d_objects}
\end{figure}

@@

To compute the total number of possible true correspondences, we take each feature in a \emph{query image} and count how many of them have a feature in the \emph{target image} which would satisfy the epipolar constraints. To avoid matching non-moving background and foreground objects we excluded features with no correspondences from being matched. This was necessary because a relatively small number of actual true correspondences between folds in the background material were mistakenly counted as false positives when evaluated which impacted the precision of test in particular on cases with few true correspondences. In practice only few feature points were excluded for this reason.

We evaluate all matching algorithms from our framework on the 3D Objects dataset by matching images at different angular intervals. For each object we pick the \emph{query} image as the image taken at 10 degrees rotation for calibration stability.  We then match this image with the same object turned an additional $\Delta$ degrees, $\Delta \in \{5, 10, \ldots, 60\}$.  For every angle interval we compare images taken under 3 different lighting conditions as provided by the dataset. We include all objects in the database for which photos at 5 degree angle intervals are available except for the ``Rooster'' and ``Sponge'' objects due to image irregularities. For each angle this means that a total of 252 image pairs are matched. We calculate the result these pairs using a weighted average based on the number of actual correspondences for each pairs. This ensures that image pairs that are more difficult to match are not contributing less to the end result because less actual matches would be found.

\subsection{Evaluation of Fast-Match on partially overlapping scenes}
\label{patches}
%
\begin{figure}[htb]
    \centering
    \begin{subfigure}[t]{0.20\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{images/acr/boat1}
    \end{subfigure}%
    ~ %
    \begin{subfigure}[t]{0.20\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{images/acr/graf1}
    \end{subfigure}%
    ~ %
    \begin{subfigure}[t]{0.24\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{images/acr/bark1}
    \end{subfigure}%
    ~ %
    \begin{subfigure}[t]{0.23\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{images/acr/wall1}
    \end{subfigure}%
    \vspace{1.5 mm}

    \begin{subfigure}[t]{0.20\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{images/acr/boat4}
    \end{subfigure}%
    ~ %
    \begin{subfigure}[t]{0.20\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{images/acr/graf3}
    \end{subfigure}%
    ~ %
    \begin{subfigure}[t]{0.24\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{images/acr/bark4}
    \end{subfigure}%
    ~ %
    \begin{subfigure}[t]{0.21\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{images/acr/wall6}
    \end{subfigure}%
    ~
    \vspace{1.5 mm}

    \caption{Four image pairs from the Graffiti dataset by Mikolajczyk et al.\ \cite{mikolajczyk2005performance}. From left to right the images are `Boat', `Graf', `Bark' and `Wall'.}
    \label{fig:patch_objects}
\end{figure}
To evaluate how well \emph{Fast-Match} handles partially overlapping scenes we make use of four images from the Graffiti dataset by Mikolajczyk et al.\ \cite{mikolajczyk2005performance} as displayed in Figure\ \ref{fig:patch_objects} all featuring challenging perspective change. For each of the four image pairs we generate a hundred pairs of smaller crops each crop randomly positioned within the original image. This process ensures that image pairs that does not contain any overlap in scene are still visually similar, making it more challenging for a matching algorithm to avoid false positives, i.e. matching local image features that are not true correspondences.

In practice the amount of overlap between pairs in a test set will 
depend on the overlap and viewpoint change in the source image pair.  To 
give a rough idea, Table~\ref{table:overlap} shows the overlap of patch 
pairs created from images 1 and 3 of the \emph{Graf} image.

\begin{table}[htb]
\caption{Overlap in the set of 100 patch pairs created from the `Graf' image pair (Figure~\ref{fig:patch_objects}).}
\label{table:overlap}
	\centering
%	\small
\begin{tabular}{r*{3}{r}}
\hline
	Amount of overlap: & 0\% & $< 50$\% & $> 50$\%  \\
	\noalign{\smallskip}
	%
	Number of patch pairs: & 21 & 54 & 25 \\
	\hline
\end{tabular}
\end{table}

Given a potential match between two pixels $p_1$ and 
$p_2$, $m = \left(p_1, p_2\right)$, and a homography $H$ relating the two images $I_1$ and $I_2$, we 
can calculate if $m$ is an inlier by checking if the two points satisfy the following criteria:
\begin{equation*}
\left\vert H p_1 - p_2 \right\vert + \left\vert H^{-1}p_2 - p_1 \right\vert < d_{\max}
\end{equation*}
That is, the distance between $p_1$ translated to $I_2$ and $p_2$ 
\emph{plus} the distance between $p_2$ translated to $I_1$ should be 
less than a certain threshold (we use $d_{\max}=5$ pixels here).

As with the 3D Objects we accumulate results across the hundred image crop pairs by using an average weighted by the amount of true correspondences between each cropped pair. This ensures that difficult to match and trivial image pairs have an equal impact on the evaluation result despite the difficult image pairs yielding far less actual matches.

\subsection{Configuration of Fast-Match}
%
The central parameters of \emph{Fast-Match} are the confidence threshold $\tau$ for selecting seed matches and the final confidence threshold applied to the total set of matches. For the experiments we let $\tau = 0.9$ and created precision/recall plots by varying the confidence threshold over the final set of matches.

To achieve a good balance between speed and robustness we let the region in which we extract features be a square window with a side length of 90 pixels. From empirical tests we found that this number works well with the SIFT feature descriptor, but for other descriptors different numbers might lead to better performance. The window is split in to nine smaller squares (see also Figure~\ref{fig:exploration}). When a seed match falls in any of these squares we match only the features within the smaller square. We let both the regions and the smaller squares overlap each other at all edges with 25 pixels in order to capture feature points lying close to an edge. For the image we have already cached we find all features within a radius of 50 pixels of the seed match.

\section{Results}
\label{results}
%
\begin{figure}[t]
\centering
\includegraphics[width=1\columnwidth]{images/grid_match_all}
\caption{Results for the 3D Objects dataset. Each plot contains the
average precision and recall over 84 objects photographed under 3 different lighting conditions weighted over the number of true correspondences for each pair.}
\label{fig:all_objects}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=1\columnwidth]{images/patches_all_horz}
\caption{Results for the Graffiti dataset. Each plot contains the
average result over 100 semi overlapping image patches based on the same
two images weighted over the number of true correspondences for each pair.}
\label{fig:patches}
\end{figure}

In Figure~\ref{fig:patches} we see the performance of the three different matching methods over 400 crop pairs based on four image pairs. As for the 3D Objects the results are shown in a precision-recall plot weighted by the number of possible true correspondences for the individual crop pairs.

At low recall we see a similar performance across all algorithms, but as the algorithms return more matches, \emph{Fast-Match} shows drastically better precision at similar recall levels than \emph{Mirror-Match} and \emph{Ratio-Match}. While this difference is more noticeable in the case of the `Bark' and `Boat' images, the `Graf' and `Wall' also see a drastic improvement in recall but as precision is lower in general for these two images the effect is less visible.

For all four image pairs we see a precision dip at very low recall which is explained by the presence of image crop pairs with no or little overlap. When matching these pairs we might often find matches even though there are no or few possible true correspondences which in effect negatively impacts the results at very low recall rates.

\begin{figure}[tb]
    \centering
    \includegraphics[width=1\columnwidth]{images/timings}
    \caption{The duration in seconds of different variations of
    \emph{Fast-Match} and \emph{Ratio-Match}. The top plot shows results
for two 10~MPixel images two 3~Mpixel images is used for the comparison
at the bottom. From the left, the first two results presume a precached
image while the rest do not require knowing any inputs beforehand. The
image pairs used can be seen in Figure~\ref{fig:match_example}}
    \label{fig:timings}
\end{figure}

@@

We have introduced \emph{Fast-Match} in two forms, a general and a retrieval variation. The retrieval variation assumes that we know one of the images that we are matching ahead of time in order to pre-cache feature points. The general variation has no assumptions and performs the pre-caching of feature points online instead. 
We have proven that while the general variation has a computational complexity of $O(n \log n)$ with $n$ being the number of feature points, the retrieval variation will on average run in $O(n)$.
From experiments on large images we have shown that \emph{Fast-Match} can be a magnitude faster than \emph{Ratio-Match} while providing comparable results. We further compared \emph{Fast-Match} to \emph{Ratio-Match} and \emph{Mirror-Match} using images of rotated 3D objects to demonstrate that \emph{Fast-Match} outperforms the other algorithms significantly over 3024 image pairs and in most cases doubles the matching precision at similar recall rates. We show that these results hold true for matching cases featuring partial or no overlap by comparing \emph{Fast-Match} on 400 crop pairs of planar scenes.
\emph{Fast-Match} is particularly applicable in cases where we are interested in matching one image to multiple large images, in which case we can quickly pre-cache the image and use this data for each of the other images.

\bibliographystyle{ieee}
\bibliography{bibliography}
\end{document}
